The software and hardware as applicable (the “Product”) described in this 
document, and this document, are protected by copyright laws, patents and 
other intellectual property laws and international treaties. The Product 
described in this document is provided pursuant to a license agreement, 
evaluation agreement and/or non-disclosure agreement. The Product may be 
used only in accordance with the terms of such agreement. The software as 
applicable may be copied only in accordance with the terms of such 
agreement.

Onload is licensed under the GNU General Public License (Version 2, June 
1991). See the LICENSE file in the distribution for details. The Onload 
Extensions Stub Library is Copyright licensed under the BSD 2-Clause 
License.

Onload contains algorithms and uses hardware interface techniques which 
are subject to Solarflare Communications Inc patent applications. Parties 
interested in licensing Solarflare's IP are encouraged to contact 
Solarflare's Intellectual Property Licensing Group at:

Director of Intellectual Property Licensing\\
Intellectual Property Licensing Group\\
Solarflare Communications Inc,//
7505 Irvine Center Drive\\
Suite 100\\
Irvine, California 92618

You will not disclose to a third party the results of any performance 
tests carried out using Onload or EnterpriseOnload without the prior 
written consent of Solarflare.

The furnishing of this document to you does not give you any rights or 
licenses, express or implied, by estoppel or otherwise, with respect to 
any such Product, or any copyrights, patents or other intellectual 
property rights covering such Product, and this document does not contain 
or represent any commitment of any kind on the part of SOLARFLARE 
Communications, Inc. or its affiliates.

The only warranties granted by SOLARFLARE Communications, Inc. or its 
affiliates in connection with the Product described in this document are 
those expressly set forth in the license agreement, evaluation agreement 
and/or non-disclosure agreement pursuant to which the Product is provided. 
EXCEPT AS EXPRESSLY SET FORTH IN SUCH AGREEMENT, NEITHER SOLARFLARE 
COMMUNICATIONS, INC. NOR ITS AFFILIATES MAKE ANY REPRESENTATIONS OR 
WARRANTIES OF ANY KIND (EXPRESS OR IMPLIED) REGARDING THE PRODUCT OR THIS 
DOCUMENTATION AND HEREBY DISCLAIM ALL IMPLIED WARRANTIES OF 
MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NON-INFRINGEMENT, 
AND ANY WARRANTIES THAT MAY ARISE FROM COURSE OF DEALING, COURSE OF 
PERFORMANCE OR USAGE OF TRADE. Unless otherwise expressly set forth in 
such agreement, to the extent allowed by applicable law (a) in no event 
shall SOLARFLARE Communications, Inc. or its affiliates have any liability 
under any legal theory for any loss of revenues or profits, loss of use or 
data, or business interruptions, or for any indirect, special, incidental 
or consequential damages, even if advised of the possibility of such 
damages; and (b) the total liability of SOLARFLARE Communications, Inc. or 
its affiliates arising from or relating to such agreement or the use of 
this document shall not exceed the amount received by SOLARFLARE 
Communications, Inc. or its affiliates for that copy of the Product or 
this document which is the subject of such liability.

The Product is not intended for use in medical, life saving, life 
sustaining, critical control or safety systems, or in nuclear facility 
applications.